Equalizer\\Programming and User Guide

### 2012-02-01 Developer/ProgrammingGuide/paper.tex
Update 1.2 PG

\date{
  \vspace{14cm}
\begin{textblock}{}(0,4.5)
  \hspace{-1cm}\includegraphics[width=22cm]{images/teaser.pdf}
\end{textblock} {\Large The official reference for developing and
  deploying parallel, scalable OpenGL\texttrademark\ applications using
  the Equalizer parallel rendering framework}\\\vspace{1cm}
Version 1.8.5 for Equalizer 1.2 \\[\medskipamount]
%  \today
}

@@

\clearpage
\pagenumbering{roman}
\pagestyle{headings}
\tableofcontents
%\clearpage
\listoffigures \vfill
\section*{Revision History}
{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Revision for Equalizer 0.5\\
    1.4     & Nov 25, 2008 & Revision for Equalizer 0.6\\
    1.6     & Aug 07, 2009 & Revision for Equalizer 0.9\\
    1.8     & Mar 21, 2011 & Revision for Equalizer 1.0\\
    1.8.1   & Mar 25, 2011 & Minor Revision\\
    1.8.2   & Apr 04, 2011 & Added \sref{sFocusDistance}\\
    1.8.3   & Aug 10, 2011 & Rewrote \sref{sHello}\\
    1.8.4   & Nov 18, 2011 & Added \sref{sAutoConfig}\\
    1.8.5   & Jan 27, 2012 & RC review for Equalizer 1.2\\
    \hline
  \end{tabularx}}
\clearpage

@@

@@

Statistics are measured in milliseconds since the configuration was
initialized. The server synchronizes the per-configuration clock on each node
automatically. Each statistic event records the originator's (channel, window,
pipe, node, view or config) unique identifier.

@@

\begin{wrapfigure}{r}{.618\textwidth}
  \includegraphics[width=.618\textwidth]{images/statistics}
  {\caption{\label{fStatistics}Statistics for a two node 2D compound}}
\end{wrapfigure}
The events are processed by the channel's and window's \textsf{processEvent}
method. The default implementation sends these events to the config using
\textsf{Config::sendEvent}, as explained in \sref{sEventHandling}. When the
default implementation of \textsf{Config::handleEvent} receives the statistics
event, it sorts the event per frame and per originator. When a frame has been
finished, the events are pushed to the local (app-)node for
visualization. Furthermore, the server also receives these event which will be
used to implement the various runtime adjustments by the equalizers.

@@

\begin{wrapfigure}{r}{.618\textwidth}
  \includegraphics[width=.618\textwidth]{images/netNode.pdf}
  {\caption{\label{fNetNode}Communication between two Nodes}}
\end{wrapfigure}
The \textsf{co::Node} is the abstraction of one process in the cluster. Each
node has a universally unique identifier. This identifier is used to address
nodes, e.g., to query connection information to connect to the node. Nodes use
connections to communicate with each other by sending packets sub-classed from
\textsf{co::NodePacket}.

The \textsf{co::LocalNode} is the specialization of the node for the given
process. It encapsulates the communication logic for connecting remote nodes, as
well as object registration and mapping. Local nodes are set up in the listening
state during initialization.

>>>>

\date{
  \vspace{14cm}
\begin{textblock}{}(0,4.5)
  \hspace{-1cm}\includegraphics[width=22cm]{images/teaser.pdf}
\end{textblock} {\Large The official reference for developing and
  deploying parallel, scalable OpenGL\texttrademark\ applications using
  the Equalizer parallel rendering framework}\\\vspace{1cm}
Version 1.8.6 for Equalizer 1.2\\[\medskipamount]
%  \today
}

@@

\clearpage
\pagenumbering{roman}
\pagestyle{headings}
\tableofcontents
%\clearpage
\listoffigures \vfill
\section*{Revision History}
{\center\begin{tabularx}{\textwidth}{|l|l|X|}
    \hline
    \bf Rev & \bf Date     & \bf Changes \\
    \hline
    1.0     & Oct 28, 2007 & Initial Version for Equalizer 0.4\\
    1.2     & Apr 15, 2008 & Revision for Equalizer 0.5\\
    1.4     & Nov 25, 2008 & Revision for Equalizer 0.6\\
    1.6     & Aug 07, 2009 & Revision for Equalizer 0.9\\
    1.8     & Mar 21, 2011 & Revision for Equalizer 1.0\\
    1.8.1   & Mar 25, 2011 & Minor Revision\\
    1.8.2   & Apr 04, 2011 & Added \sref{sFocusDistance}\\
    1.8.3   & Aug 10, 2011 & Rewrote \sref{sHello}\\
    1.8.4   & Nov 18, 2011 & Added \sref{sAutoConfig}\\
    1.8.5   & Jan 27, 2012 & RC review for Equalizer 1.2\\
    1.8.6   & Feb 01, 2012 & RC2, added to \sref{sThreadModel}\\
    \hline
  \end{tabularx}}
\clearpage

@@

An implication of the draw\_sync and local\_sync models is that the application
node can not issue a new frame until it has completed all its draw tasks. For
larger cluster configurations it is therefore advisable to assign only assemble
operations to the application node. If the machine running the application
process should also contribute for rendering, a second node may be used to
perform off-screen draw and readback operations for the application node
process.

@@

\begin{wrapfigure}{r}{.618\textwidth}
  \includegraphics[width=.618\textwidth]{images/statistics}
  {\caption{\label{fStatistics}Statistics for a two node 2D compound}}
\end{wrapfigure}
Statistics are measured in milliseconds since the configuration was
initialized. The server synchronizes the per-configuration clock on each node
automatically. Each statistic event records the originator's (channel, window,
pipe, node, view or config) unique identifier.

@@

The events are processed by the channel's and window's \textsf{processEvent}
method. The default implementation sends these events to the config using
\textsf{Config::sendEvent}, as explained in \sref{sEventHandling}. When the
default implementation of \textsf{Config::handleEvent} receives the statistics
event, it sorts the event per frame and per originator. When a frame has been
finished, the events are pushed to the local (app-)node for
visualization. Furthermore, the server also receives these event which will be
used to implement the various runtime adjustments by the equalizers.

@@

The \textsf{co::Node} is the abstraction of one process in the cluster. Each
node has a universally unique identifier. This identifier is used to address
nodes, e.g., to query connection information to connect to the node. Nodes use
connections to communicate with each other by sending packets sub-classed from
\textsf{co::NodePacket}.

\begin{wrapfigure}{r}{.618\textwidth}
  \includegraphics[width=.618\textwidth]{images/netNode.pdf}
  {\caption{\label{fNetNode}Communication between two Nodes}}
\end{wrapfigure}
The \textsf{co::LocalNode} is the specialization of the node for the given
process. It encapsulates the communication logic for connecting remote nodes, as
well as object registration and mapping. Local nodes are set up in the listening
state during initialization.
